IRTF Spectro-Photometry of Two Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-11-11 ms.tex
Some text updates throughout and I added a few acknowledgements.

\title{IRTF Spectro-Photometry of Rotating Brown Dwarfs}

@@

\begin{abstract}
L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres. We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010, both of spectral type L4-L5. 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m. 2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m, that can be fit by Mie extinction of sub-micron dust particles.
\end{abstract}

@@

We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
In this simple model, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
We model the extinction coefficient from the \texttt{IDL} Mie theory code \texttt{mie\_single.pro} \citep{grainger04} to calculate the extinction as a function of wavelength.
We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains.
For the particle size distribution we assume a log-normal distribution around a characteristic size with a distribution $\sigma$ of 0.5.

@@

Our model best-fits the data with $\alpha_i$ << 1 and also with much lower temperatures than equilibrium, shown in Figure \ref{fig:ampspec1821tdiff}.
This model has a reduced chi-squared of 1.3, consistent with the data, but not with the effective temperature.
If we restrict the model to be a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures, the best-fit is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a $\bar{\chi}^2$ = 15.
Finally, we attempt a model where we restrict the temperature limits to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{citet{gagne2015banyan7}}.
The best fit model has $T_{eff} \approx $1590 K, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
This model fits with $\bar{\chi}^2$ = 2.1.
However, the temperature contrasts in these models are significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.

@@

We observed two brown dwarfs of spectral type L4-L5: 2MASS 1821 and 2MASS 0835.
These brown dwarfs have temperatures near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$.
We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems.
After fitting sinusoids to both of the time series, we find that the

\section{Acknowledgements}
%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

>>>>

\title{IRTF Spectro-Photometry of Two Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010}

@@

\begin{abstract}
L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres. We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010, both of spectral type L4-L5 using the Infrared Telescope Facility (IRTF). 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m. 2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m, that can be fit by Mie extinction of sub-micron dust particles. It can also be fit by a hot spots on the brown dwarf surface, but they require implausible temperature variations, so we prefer the Mie scattering model.
\end{abstract}

@@

We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
In this simple model, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
We model the extinction coefficient, $Q_{ext}$ from the \texttt{IDL} Mie theory code \texttt{mie\_single.pro} \citep{grainger04} to calculate the extinction as a function of wavelength.
We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains (MgSiO$_3$).
For the particle size distribution we assume a log-normal distribution around a characteristic size with a distribution $\sigma$ of 0.5.

@@

Our model best-fits the data with $\alpha_i << $1 and also with much lower temperatures than equilibrium, shown in Figure \ref{fig:ampspec1821tdiff}.
This model has a reduced chi-squared of 1.3, consistent with the data, but not with the effective temperature.
If we restrict the model to be a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures, the best-fit is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a $\bar{\chi}^2$ = 15.
Finally, we attempt a model where we restrict the temperature limits to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
The best fit model has $T_{eff} \approx $1590 K, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
Therefore, we suspect that hot or cold spots on the surface a are a less likely scenario to explain the variability of 2MASS 1821.

@@

We observed two brown dwarfs of spectral type L4-L5: 2MASS 1821 and 2MASS 0835.
These brown dwarfs have temperatures near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$.
We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems with the IRTF.
After fitting sinusoids to both of the time series, we find that 2MASS 0835 is not variable to within measurement precision.

\section{Acknowledgements}
Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature model.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.

%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.
